---
title: "penguin_investigations"
author: "jgh"
format: html
editor: visual
---


Let's look at some penguin morphology courtesy of Palmer:

```{r}
 #| echo: false
library(palmerpenguins)
library(tidyverse)
library(magrittr)

head(penguins)
```

Let's look at some of the differences in body size by species, shall we?

```{r}
penguins %>% group_by(species) %>%
	summarise(n = n(), mass = mean(body_mass_g, na.rm = T), se = sd(body_mass_g, na.rm = T)/sqrt(n))
```

It looks like Adelie and Chinstrap are roughly the same size, but Gentoo are substantially larger. Is that a function of skeletal size or are Gentoo just chunkier? Let's see how body mass is related to skeletal morphometrics:

```{r}
#| echo: false

library(viridis)

ggplot(penguins, aes(x = flipper_length_mm/10, y = body_mass_g/1000, colour = species)) +
	geom_point() +
	geom_smooth(method = 'lm') +
	scale_colour_viridis(option = "D", begin = 0.9, end = 0.2, discrete = TRUE) +
	xlab("Flipper length (cm)") +
	ylab("Body mass (kg)") +
	theme_light()

```

The Gentoo are larger in terms of limb size as well, and maybe also have a steeper slope of this relationship? Hard to know for sure...

```{r}
#| echo:false
#| 
summary(lm(body_mass_g ~ species*flipper_length_mm, data = penguins))
```

The interaction is significant: Adelie and Chinstrap both increase in body size along with flipper size, but for Gentoo, this slope is steeper (approx. 66% more g of body mass added per mm of flipper length). neat!

